Figure 2 and figure 2 supplementary material

### 2022-06-23 Figures/Figures_nonTCGA.Rmd
add Figures_nonTCGA.Rmd
corrected teh celltype estimations~ground truth equivalences. Yet to fix
the corrplot function

################################################################################
wrapper_tpurity <- function(deconv_data, true_estimates, estimate, cancer_abreviation){
  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_

  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
                                         true_subset_$Sample_ID))
  true_subset_ %>% 
    dplyr::filter(Sample_ID %in% Comm_samples) %>% 
    arrange(factor(Sample_ID, levels = Comm_samples)) -> true_subset

  deconv_data %>% 
    dplyr::filter(Samples %in% Comm_samples) %>% 
    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset

  # Scatterplot CCLE_TIL10
  identical(true_subset$Sample_ID, deconv_subset$Samples) %>% stopifnot()
   true_subset %>% bind_cols(deconv_subset) -> merged_subset

  final_plot = list()
  color = "black"
  x_lab = estimate

  title = paste0(estimate, " vs CCLE TIL10 Cancer")
  y_lab = "CCLE TIL10 Cancer"
  final_plot[["ccle"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_CCLE_TIL10_Cancer.cells", title, color,  x_lab, y_lab)

  # Scatterplot BPRNACan
  title = paste0(estimate, " vs BPRNACan Cancer")
  y_lab = "BPRNACan Cancer"
  final_plot[["bprnacan"]] <- scatterplot_truevsestimate(merged_subset, estimate, "Epidish_BPRNACan_cancer", title, color, x_lab, y_lab)

  return(final_plot)
}
################################################################################

################################################################################
# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
# of a given method/signature.
# Works inside of ridgeplot_parse. it takes:
# -  'deconv_data': contains the deconvolution data to index and summarize. 
#
# -  'signature dictionary': contains the exact names of the method
#                           (if it works with one signature) or the signature
#                           (if it works with multiple methods). 
#
# - iterator: string to subscript the signatures_dict with either signature
#             or methods names depending where is it called
#
# - prefix: string to leave just celltype names when substracted to the columns
#             of deconv_data of the specified method (or method + signature).
#
# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"

ridgeplot_parse <- function(deconv_data, signatures_dictionary){

  results <- tibble(Samples = deconv_data$Samples)

  names_table <- deconv_data %>%
    dplyr::select(-c(Samples)) %>%
    names() %>%
    str_split_fixed("_", 2) %>%
    as_tibble(.name_repair = "unique")

  for (method in unique(names_table[,1,drop=T])){

    if (method %in% c("Epidish",
                      "DeconRNASeq",
                      "CBSX")){

      for (signature in names(signatures_dictionary)){ # iterates through all the signatures (the ones not present for the method will yield all 0)
        to_match <- paste(method, signature, sep = "_")

        for (celltype in names(signatures_dictionary[[signature]])){
          if (length(signatures_dictionary[[signature]][[celltype]]) > 0){
            name_of_summary <- paste(to_match, celltype, sep = "_")
            columns_to_summarize <- paste(to_match, signatures_dictionary[[signature]][[celltype]], sep = ".")
            # print(name_of_summary)
            # deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% colnames() %>% print()
            # cat("-------------------------\n")
            deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
          }
        }
  }
    } else{

    to_match <- method

    for (celltype in names(signatures_dictionary[[method]])){
      if (length(signatures_dictionary[[method]][[celltype]]) > 0){
          name_of_summary <- paste(to_match, celltype, sep = "_")
          columns_to_summarize <- paste(to_match, signatures_dictionary[[method]][[celltype]], sep = ".")

          deconv_data %>% dplyr::select(matches(columns_to_summarize)) %>% rowSums(.) -> results[name_of_summary]
      }
    }
  }
  }
  results %>% dplyr::select(-Samples) %>% dplyr::select(which(!colSums(., na.rm=TRUE) %in% 0)) %>% bind_cols(Samples = results$Samples,.)
}
################################################################################

################################################################################
plot_ridgeplot <- function(data){
 data %>% dplyr::select(-c(ParticipantBarcode, Study)) %>% data.matrix() %>% rcorr() -> cor.table
  final_plot <- list()
  for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
    # select strings to remove from signature names
    substring_remove <- c(paste("_",ct, sep=""),
      "_Tirosh_sigmatrix_SuppFig_3-b",
      "_scRNA-Seq",
      "Fig2ab-",
      "_PBMCs_scRNAseq_sigmatrix",
      "sigmatrix_",
      "_Fig2cd")

    # filter correlations
    deconv_ct_names <- data %>% dplyr::select(matches(ct), -ct) %>% names()
    cor.table[["r"]][ct,deconv_ct_names] %>% sort() -> cor.ct.sorted
    names(cor.ct.sorted) <- str_remove_all(names(cor.ct.sorted), paste(substring_remove, collapse = "|"))
    cor.ct.sorted["H&E"] = 1

    # ridgeplot perse
    cols <- c("H&E" = "red", "CBSX" = "yellow", "Epidish" = "blue", "Quantiseq" = "pink", "DeconRNASeq" = "green")

    ct_subset = data %>%
      dplyr::select(matches(ct)) %>%
      dplyr::rename("H&E" = ct) %>%
      gather() %>%
      mutate(key = str_remove_all(key, paste(substring_remove, collapse = "|")),
             key=factor(key, levels=names(cor.ct.sorted)),
             method = as.factor(str_extract(key, "[^_]+")))
  adjust_x <- max(ct_subset$value)
  final_plot[[ct]] <- print(ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
    geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                         point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
    theme_ridges() + ggtitle(ct) +
    annotate("text", x = adjust_x, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
    scale_x_continuous(limits = c(0, (adjust_x + adjust_x*0.2))) +
    scale_colour_manual(values = cols) +
     theme(axis.text.x = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          axis.text.y = element_text(color = "black", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
          axis.title.x = element_text(color = "black", size = 10, angle = 0, hjust = .5, vjust = 0, face = "plain"),
          axis.title.y = element_text(color = "black", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          plot.title = element_text(color = "black", size = 20)) +
    ylab("") + xlab("% of cell type"))
  }
  return(final_plot)
}
################################################################################

################################################################################
wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){

  # build the data
  true_estimates %>% dplyr::filter(Study == cancer_abreviation) %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))  -> true_subset_

  Comm_samples <- Reduce(intersect, list(deconv_data$Samples,
                                         true_subset_$ParticipantBarcode))
  true_subset_ %>% 
    dplyr::filter(ParticipantBarcode %in% Comm_samples) %>% 
    arrange(factor(ParticipantBarcode, levels = Comm_samples)) -> true_subset

  deconv_data  %>%
    dplyr::filter(Samples %in% Comm_samples) %>% 
    arrange(factor(Samples, levels = Comm_samples)) -> deconv_subset

  deconv_subset_summary <- ridgeplot_parse(deconv_data = deconv_subset, signatures_dictionary = signature_dict)

  identical(true_subset$ParticipantBarcode, deconv_subset_summary$Samples) %>% stopifnot()
  true_subset %>% bind_cols(deconv_subset_summary) %>% dplyr::select(-c(Samples)) -> data_toplot

  # calculate correlations
 return(plot_ridgeplot(data_toplot))
}
################################################################################

################################################################################
wrapper_corrplots <- function(deconv_data, true_estimates){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))

@@

  to_corr <- bind_cols(true_subset, deconv_subset_summary) %>% dplyr::select(-c(Samples))
  ct_corrplots <- list()
   for (ct in c("Lymphocytes", "Macrophages", "Neutrophils")){
    # select strings to remove from signature names
    substring_remove <- c(paste0("_",ct),
      "_Tirosh_sigmatrix_SuppFig_3.b",
      "_scRNA.Seq",
      "Fig2ab.",
      "_PBMCs_scRNAseq_sigmatrix",
      "sigmatrix_",
      "_Fig2cd")

    store_corrs <- tibble(measure1 = character(),
                          measure2 = character(),
                          r = numeric(),
                          n = numeric(),
                          p = numeric(),
                          sig_p = logical(),
                          p_if_sig = numeric(),
                          r_if_sig = numeric())
    # segregate by cancer type
    for (st in unique(to_corr$Study)){
      deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
        # segregate by ct
        dplyr::select(matches(ct)) %>%
        formatted_cors(cor.stat = "pearson") %>%
        # reduce to corrs just to ground truth
        dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
        # rename ground truth as cancer type
        dplyr::mutate(measure1 = st)
      #add to the rest of cancer type correlations
      store_corrs <- add_row(store_corrs , deconv_ct_names)
    }

@@

    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
    rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())
   }
  return(ct_corrplots)
}

@@

```{r}
read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
  mutate_at("Samples", str_remove_all, ".01A*") %>%
  mutate_at("Samples", str_replace_all, "-", ".") %>% 
  group_by(Samples) %>%
  summarise_all(mean) -> tcga_deconv

read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Aran_facs.csv") %>%
  mutate_at("Sample_ID", str_remove_all, ".01A*") %>%
  mutate_at("Sample_ID", str_replace_all, "-", ".") -> Aran_all_facs

read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/HE_fractions.csv") %>%
  dplyr::select(-c(...1)) %>%
  mutate_at("ParticipantBarcode", str_remove_all, ".01A*") %>%
  mutate_at("ParticipantBarcode", str_replace_all, "-", ".") %>%
  distinct(ParticipantBarcode, .keep_all= TRUE) -> HE_all_TCGA # for the READ samples TCGA.AG.5 & TCGA.AG.3

@@

# Figure
## A) Tumor Purity
```{r}
wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = "ABSOLUTE" , cancer_abreviation = "LUAD")
```

## B) 3 Celltypes ridge plots
### Create aggregation dictionaries to compare with Lymphocites, Macrophages and Neutrophils FACs

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
signature_dict <- list()
signature_dict[["BPRNACan"]] <- list(Lymphocytes = c("B", "CD4", "CD8", "NK"),
                    Macrophages = c("Mono", "M0", "M1", "M2"),
                    Neutrophils = c("Neu"))

@@

signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4","NKT.cells" ,"B.cells", "NK.cells"),
                                                                         Macrophages = c("Monocytes"),
                                                                         Neutrophils = c())

signature_dict[["CBSX_LM22"]] <- list(Lymphocytes = c("B.cells.naive", "B.cells.memory",  "T.cells.CD8",
                                                        "T.cells.CD4.naive", "T.cells.CD4.memory.resting",
                                                        "T.cells.CD4.memory.activated", 
                                                        "T.cells.regulatory..Tregs.", "NK.cells.resting",
                                                        "NK.cells.activated"),
                                        Macrophages = c("Monocytes", "Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
                                        Neutrophils = c("Neutrophils")) # skipped , "Plasma.cells" "T.cells.follicular.helper", "T.cells.gamma.delta" in Lymphos, as well as "Dendritic.cells.resting", "Dendritic.cells.activated" for macros

signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4",
                                                                                                   "NK.cells", "B.cells"),
                                                                                   Macrophages = c("Macrophages"),
                                                                                   Neutrophils = c())

signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells"),
                                                          Macrophages = c("Macrophages", "Dendritic.cells"),
                                                          Neutrophils = c())

signature_dict[["CCLE_TIL10"]] <- list(Lymphocytes = c("T.cells.CD8", "T.cells.CD4", "B.cells", "NK.cells", "Tregs"),
                    Macrophages = c("Macrophages.M1", "Macrophages.M2", "Monocytes", "Dendritic.cells"),
                    Neutrophils = c("Neutrophils"))

signature_dict[["Quantiseq"]] <- list(Lymphocytes = c("B.cell", "T.cell.CD4+.(non-regulatory)", "T.cell.CD8+", "T.cell.regulatory(Tregs)", "NK.cell"),
                    Macrophages = c("Macrophage.M1", "Macrophage.M2", "Myeloid.dendritic.cell", "Monocyte"),
                    Neutrophils = c("Neutrophil"))

# signature_dict[["MCP"]] <- list(Lymphocytes = c("T.cells", "CD8.T.cells", "Cytotoxic.lymphocytes","B.lineage" ,"NK.cells"),
#                     Macrophages = c("Myeloid.dendritic.cells", "Monocytic.lineage"),
#                     Neutrophils = c("Neutrophils")) # Based in enrichment so cant sum celltype estimates

# signature_dict[["XCELL"]] <- list(Lymphocytes = c(".B-cells", "CD4+.", "CD8+.", "CLP", "NK.", "Th1_cells", "Tgd_cells", "Th2_cells", "Tregs"),
#                     Macrophages = c("aDC", "cDC", "iDC", "pDC", "DC", "Macrophages.", "Monocytes"),
#                     Neutrophils = c("Neutrophils")) # Not in the paper in theory

### Data processing & ridge plot

```{r}

tcga_deconv %>%
  rename_at(vars(matches("^CBSX")), ~ paste0("CBSX_", .)) %>% 
  rename_at(vars(matches("__")), ~ str_replace_all(., "__", "_")) -> tcga_deconv_ridge

wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = "LUAD")
```

## Summary Corrplot

```{r}
corrplots <- wrapper_corrplots(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA)
corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")

@@

# Suplementary figure
```{r}
ridgeplots_by_cancer <- list()
tpurity_by_cancer <- list()
blank  <- ggplot() + theme_void()

for (cancer in unique(HE_all_TCGA$Study)){
  ridgeplots_by_cancer[[cancer]] <- wrapper_ridgeplot(deconv_data = tcga_deconv_ridge, true_estimates = HE_all_TCGA, cancer_abreviation = cancer)
  tpurity_by_cancer[[cancer]] <- tryCatch({ wrapper_tpurity(deconv_data = tcga_deconv, true_estimates = Aran_all_facs, estimate = "ABSOLUTE", cancer_abreviation = cancer) # sometimes there arent enough samples of the tumour type
        },
        error = function(cond) {
          message(paste("not enough FACs samples for ", cancer, "no scatterplot will be generated"))
          return(list(ccle = blank, bprna = blank))
        }
  )
  tpurity_by_cancer[[cancer]]$extra = blank

  ridges <- ggarrange(plotlist = ridgeplots_by_cancer[[cancer]], ncol = 3, common.legend = T, legend = "bottom")
  scater <- ggarrange(plotlist = tpurity_by_cancer[[cancer]], ncol = 3, common.legend = T)
  blank  <- ggplot() + theme_void()
  fullplot <- ggarrange(plotlist = list(scater, ridges, blank), nrow = 3, heights = c(0.15, 0.3, 0.45))
  annotate_figure(fullplot, top = text_grob(cancer, color = "black", size = 40))
  pdf_name <- paste("Sup.fig2_", cancer, ".pdf", sep = "")
  ggsave(pdf_name, dpi = "print", width = 210, height = 297, units = "mm", scale = 2.5)
}
system("pdfunite Sup.fig2_*.pdf Sup.fig2.pdf")
```

>>>>

################################################################################
benchmark_corrplots <- function(deconv_data, true_estimates){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))

@@

  to_corr <- bind_cols(true_subset, deconv_subset_summary) %>% dplyr::select(-c(Samples))
  ct_corrplots <- list()

    for (st in unique(celltypes)){
      deconv_ct_names <- dplyr::filter(to_corr, Study == st) %>%
        # segregate by ct
        dplyr::select(matches(ct)) %>%
        formatted_cors(cor.stat = "pearson") %>%
        # reduce to corrs just to ground truth
        dplyr::filter(measure1 == all_of(ct), measure2 != all_of(ct)) %>%
        # rename ground truth as cancer type
        dplyr::mutate(measure1 = st)
      #add to the rest of cancer type correlations
      store_corrs <- add_row(store_corrs , deconv_ct_names)
    }

@@

    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
    rotate_x_text(angle = 45) + theme(axis.text.y=element_markdown())

  return(ct_corrplots)
}

@@

```{r}
deconv <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt")

ground_truth <- read.table("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Julien/gemdecan/data/facs/Facs_Melanoma_GSE72056.txt") %>% as_tibble(rownames = "Samples")

@@

# Figure
## B) 3 Celltypes ridge plots
### Create aggregation dictionaries to compare with Lymphocites, Macrophages and Neutrophils FACs

```{r}
# Lists of celltypes of each signature
## signature dictionary construction (can use . as regexp!)
## uncoment print of functions to check that you detect what you want.
## non matching signatures/methods (all 0) are removed.
signature_dict <- list()
signature_dict[["BPRNACan"]] <- list(B = c("B"),
                                     CAFs = c(""),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(""),
                                     Macrophages = c("M0", "M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(""),
                                     Treg = c(""),
                                     Cancer = c("cancer"),
                                     Other = c("Mono", "Neu"))

@@

signature_dict[["CBSX_Fig2ab-NSCLC_PBMCs_scRNAseq_sigmatrix"]] <- list(B = c("B.cells"),
                                     CAFs = c(""),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(""),
                                     Macrophages = c(""),
                                     NK = c("NK.cells"),
                                     Th = c(""),
                                     Treg = c(""),
                                     Cancer = c(""),
                                     Other = c("Monocytes","NKT.cells"))

signature_dict[["CBSX_LM22"]] <- list(B = c("B.cells.naive", "B.cells.memory", "Plasma.cells"),
                                     CAFs = c(""),
                                     CD4 = c("T.cells.CD4.naive", "T.cells.CD4.memory.resting", "T.cells.CD4.memory.activated"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c(""),
                                     Macrophages = c("Macrophages.M0", "Macrophages.M1", "Macrophages.M2"),
                                     NK = c("NK.cells.resting", "NK.cells.activated"),
                                     Th = c("T.cells.follicular.helper", "T.cells.gamma.delta"),
                                     Treg = c("T.cells.regulatory..Tregs."),
                                     Cancer = c(""),
                                     Other = c("Monocytes", "Dendritic.cells.resting", "Dendritic.cells.activated", "Mast.cells.resting", "Mast.cells.activated", "Eosinophils", "Neutrophils"))

signature_dict[["CBSX_scRNA-Seq_melanoma_Tirosh_sigmatrix_SuppFig_3-b"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAF"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c("NK.cells"),
                                     Th = c(""),
                                     Treg = c(""),
                                     Cancer = c("Malignant"),
                                     Other = c(""))

signature_dict[["CBSX_sigmatrix_HNSCC_Fig2cd"]] <- list(B = c("B.cells"),
                                     CAFs = c("CAFs"),
                                     CD4 = c("T.cells.CD4"),
                                     CD8 = c("T.cells.CD8"),
                                     Endothelial = c("Endothelial.cells"),
                                     Macrophages = c("Macrophages"),
                                     NK = c(""),
                                     Th = c(""),
                                     Treg = c(""),
                                     Cancer = c("Malignant.cells"),
                                     Other = c("Dendritic.cells", "Mast.cells", "Myocytes"))

signature_dict[["Quantiseq"]] <- list(B = c("B.cell"),
                                     CAFs = c(""),
                                     CD4 = c("T.cell.CD4+.(non-regulatory)"),
                                     CD8 = c("T.cell.CD8+"),
                                     Endothelial = c(""),
                                     Macrophages = c("Macrophage.M1", "Macrophage.M2"),
                                     NK = c("NK.cell"),
                                     Th = c(""),
                                     Treg = c("T.cell.regulatory(Tregs)"),
                                     Cancer = c(""),
                                     Other = c("Monocyte", "Neutrophil", "Myeloid.dendritic.cell", "uncharacterized.cell"))

# signature_dict[["CCLE_TIL10"]] <- list(B = c("B"),
#                                      CAFs = c(""),
#                                      CD4 = c(""),
#                                      CD8 = c(""),
#                                      Endothelial = c(""),
#                                      Macrophages = c(""),
#                                      NK = c(""),
#                                      Th = c(""),
#                                      Treg = c(""),
#                                      Cancer = c(""),
#                                      Other = c(""))

# signature_dict[[""]] <- list(B = c(""),
#                                      CAFs = c(""),
#                                      CD4 = c(""),
#                                      CD8 = c(""),
#                                      Endothelial = c(""),
#                                      Macrophages = c(""),
#                                      NK = c(""),
#                                      Th = c(""),
#                                      Treg = c(""),
#                                      Cancer = c(""),
#                                      Other = c(""))

```
## Summary Corrplot

```{r}
corrplots <- benchmark_corrplots(deconv_data = deconv, true_estimates = ground_truth)
corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")

@@
